Figures

### 2019-07-26 figures/09_stream_buffer.Rmd
figure cleanup

llids <- c("6992", "7026")

@@

i <- 1
gg_low_ag <- ggplot() + 
  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  ggtitle(llids[i])

i <- 2
gg_hi_ag <- ggplot() + 
  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  ggtitle(llids[i])

>>>>

llids         <- c("6992", "7026")
lg            <- lagosne_load("1.087.1")
llid_metadata <- lake_info(llids, dt = lg)
llid_callouts <- paste(llid_metadata$gnis_name, "-", llid_metadata$state)

@@

### draw forest outlines
# i <- 2
# forest_outline <- mapedit::editMap(
#   mapview(images[[i]])
#   )
# forest_outline <- smoothr::smooth(forest_outline$drawn)
# forest_outline <- st_intersection(
#   st_transform(forest_outline, st_crs(res_iws[i,])),
#   res_iws[i,])
# mapview(forest_outline)
# saveRDS(forest_outline, "../data/res_forest_outline_2.rds")
# forest_outline_1 <- readRDS("../data/res_forest_outline_1.rds")
# forest_outline_2 <- readRDS("../data/res_forest_outline_2.rds")

i <- 1
rs <- prep_ggplot_raster(images[[i]], res_iws[i,])
gg_low_ag <- ggplot() + 
  geom_raster(data = rs, 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
  # geom_sf(data = forest_outline_1, color = "green3") +
  geom_sf(data = st_difference(
      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
      res_lakes[i,]), 
    color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  annotate("text", label = llid_callouts[i], x = median(rs$x), 
           y = min(rs$y))

i <- 2
rs <- prep_ggplot_raster(images[[i]], res_iws[i,])
gg_hi_ag <- ggplot() + 
  geom_raster(data = rs, 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
  # geom_sf(data = forest_outline_2, color = "green3") +
  geom_sf(data = st_difference(
      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
      res_lakes[i,]), 
    color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  annotate("text", label = llid_callouts[i], x = median(rs$x), 
           y = min(rs$y))
